Titeln på avhandlingens språk

### 2022-11-06 sampling.tex
Update on Overleaf.

>>>>

Now, we modify the problem (see section \ref{sec:aprxSol_Energy_samples}) and find the optimum sampling instants that minimises the expected number of samples for a given upper bound for the expected wait time. First note that, the general solution has constants $\alpha$ and $\beta$ that corresponds to the weights given to the cost of sampling and cost of waiting, respectively. The optimisation criteria changes from minimising wait time to minimising the number of samples, when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity. As any positive real value is valid for this ratio, we can argue that any optimisation problem -- constrained or unconstrained -- can be boiled down to thewith all possible real values in between

We do this by equating \cref{Ew} to $w_0$ and find the ratio of $\frac{\alpha}{\beta}$ that provides the optimum set of sampling instants when plugged into \cref{tnFinal}. This is possible because, wit
For this, we make use of the facts that
\begin{enumerate*}[itemjoin={{, }}, itemjoin*={{, and }}]
    \item the bound will be tight at the optimum due to the continuous nature of possible sampling instants and sampling intervals
    \item one can achieve any arbitrary point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via the unconstrained optimization discussed above simply by varying the ratio $\frac{\alpha}{\beta}$.
\end{enumerate*}
\begin{alignat*}{1}
\mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber\\
&=\int_{0}^{\infty}\frac{1}{2}\sqrt{\frac{2\alpha\sigma^2}{\beta t}}\cdot \frac{t}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\int_{0}^{\infty}\frac{\sqrt{t}}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\int_{0}^{\infty}y^{-1/4}e^{-y}\mathrm{d}y\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\mathlarger{\Gamma}(\tfrac{3}{4})\\
% &\approx 0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
\intertext{Thus, when the upper bound $w_0$ is tight,}
w_0&=0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
w_0&=\sqrt{\frac{\alpha\sigma}{2\sqrt{2}\beta}}\mathlarger{\Gamma}(\tfrac{3}{4})\\
\Rightarrow\frac{\alpha}{\beta}&=\frac{w_0^2}{\sigma}\frac{2\sqrt{2}}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2}\\&=1.88355\frac{w_0^2}{\sigma}
\end{alignat*}
